---
title: "Computational calculation and visualization of the Biological Value Index"
author:
  - Juan Carlos Villaseñor-Derbez^[Bren School, john@example.org]
  - Ricardo Dominguez-Reza^[CICESE, jane@example.org]
  - Los que falten
output:
  bookdown::pdf_document2:
    fig_caption: yes
    fig_width: 5
    keep_tex: yes
abstract: "Abstract goes here"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)

suppressPackageStartupMessages({
  library(knitr)
  library(kableExtra)
  library(magrittr)
  library(tidyverse)
})

```

#Introduction

Todo esto es mierda, tengo que modificarlo

- Indices in ecology

Usually people describe a site by the species that inhabit it, but do not pay much attention to how some species are incharged of the simmilarities.

- History of the index
	  - When it was proposed
	  - How it worked
	  - Modifications by Loya Salinas
	  - How it works now
	
- Usage of the index 
	  - Works that have used it
	
- Stating the problem
    - Lack of comparison
    - computability

# Materials and Methods

```{r}
data <- read_csv(here::here("data", "data.csv"), col_types = cols())
```


- How the index works, step by step (possibly citing Loya-Salinas)

- Flow diagram depfun(ivb)

- Adding the %BVI

\begin{equation}\%BVI_i = \frac{(100\times BVI_i)}{\sum_{i = 1}^nBVI_i}\end{equation}

- Compare N and Ni vs rBVI to test its usefulness

- Propose ways to visualize rBVI

- Recreating Loya-Salinas

```{r}
source(here::here('bvi.R'))
source(here::here('bvi_plot.R'))
source(here::here('bvi_col.R'))
source(here::here('bvi_boxplot.R'))
```

	
```{r}
data %>% 
  kable(digits = 2,
        format = "latex",
        booktabs = T) %>% 
  kableExtra::column_spec(column = 1,
                          italic = T)
```

- Mention using SIMPER as a comparative
- Propose a graph to visualize data

# Results

- Results from Loya-Salinas
- Graph
- Comparing %BVI with SIMPER
- Table with abundances, BVI, %BVI and SIMPER

```{r}
bvi(data) %>% 
  rbind(data.frame(Spp = "Total",
                   S1 = "",
                   S2 = "",
                   S3 = "",
                   S4 = "",
                   S5 = "",
                   S6 = "",
                   BVI = "",
                   rBVI = 100,
                   stringsAsFactors = F)) %>% 
  knitr::kable(digits = 2,
               format = "latex",
               booktabs = T, 
               col.names = c("Species", "S1", "S2", "S3", "S4", "S5", "S6", "BVI", "%BVI")) %>% 
  kableExtra::column_spec(column = 1,
                          italic = T)
```

```{r}
rel_abundance <- data %>%
  gather(Sample, Abundance, -Spp) %>% 
  group_by(Sample) %>% 
  summarize(N = sum(Abundance))

abundances <- data %>% 
  gather(Sample, Abundance, -Spp) %>% 
  left_join(rel_abundance, by = "Sample") %>% 
  mutate(RelAbundance = Abundance/N,
         Abundance = log10(Abundance)) %>% 
  select(-N) %>% 
  filter(Abundance > 0)

shortSpp <- data.frame(Species = c("Synchelidium spp.", "Tridentella spp.", "N. cirratulus", "N. californiensis", "G. tenuis", "D. gouldii", "O. benedicti", "Archaeomysis spp.", "Armadillium spp.", "Megalopus spp.", "E. analoga", "Pontharpinia spp.", "E. mucronata", "L. californica", "M. californica", "Hanstorina spp.", "G. dibranchiata", "A. maculata"), 
                       Spp = c("Synchelidium spp.", "Tridentella spp.", "Nerine cirratulus", "Nephtys californiensis", "Glycera tenuis", "Donax gouldii", "Orchestoidea benedicti", "Archaeomysis spp.", "Armadillium spp.", "Megalopus spp.", "Emerita analoga", "Pontharpinia spp.", "Euzonus mucronata", "Lepidopa californica", "Magelona californica", "Hanstorina spp.", "Glycera dibranchiata", "Archaeomysis maculata"), stringsAsFactors = F)

compare_indices <- data %>% 
  bvi(others = F) %>% 
  select(Spp, BVI, rBVI) %>% 
  left_join(abundances, by = "Spp") %>% 
  left_join(shortSpp, by = "Spp")
```


```{r, results = "asis"}
model1 <- lm(RelAbundance ~ rBVI, data = compare_indices)
model2 <- lm(Abundance ~ rBVI, data = compare_indices)


stargazer::stargazer(model1, model2,
                     header = F,
                     single.row = T, 
                     keep.stat = c("f", "n", "rsq", "ser", "wald"), dep.var.labels = c("%N", "log10(n)"))
```

\clearpage

```{r, fig.width = 6.5, fig.height = 6.5}
p1 <- compare_indices %>% 
  ggplot(aes(x = rBVI/100, y = RelAbundance)) +
  geom_smooth(method = "lm", color = "black", linetype = "dashed", alpha = 0.3) +
  geom_point(aes(fill = Species), pch = 21, color = "black", size = 2, alpha = 0.5) +
  theme_bw() +
  scale_x_continuous(labels = scales::percent) +
  labs(x = "relative BVI", y = "%N") +
  geom_text(aes(x = 0, y = 0.75, label = "b)")) +
  theme(text = element_text(size = 10),
        legend.justification = c(0.5, 1),
        legend.position = c(0.5,1.05),
        legend.background = element_rect(fill = "transparent"),
        legend.title = element_blank(),
        legend.text = element_text(size = 8),
        legend.key = element_rect(fill = "transparent")) +
  guides(fill = guide_legend(ncol = 4))

p2 <- compare_indices %>% 
  ggplot(aes(x = rBVI/100, y = Abundance)) +
  geom_smooth(method = "lm", color = "black", linetype = "dashed", alpha = 0.3) +
  geom_point(aes(fill = Species), pch = 21, color = "black", size = 2, alpha = 0.5) +
  theme_bw() +
  scale_x_continuous(labels = scales::percent) +
  labs(x = "relative BVI", y = "log10(n)") +
  geom_text(aes(x = 0, y = 3.75, label = "a)")) +
  labs(x = "") +
  theme(text = element_text(size = 10),
        legend.position = "None")

gridExtra::grid.arrange(p1, p2)
```

```{r, fig.width = 6.5, fig.height = 6.5}
plot2 <- data %>% 
  bvi() %>% 
  bvi_col()

plot3 <- data %>% 
  bvi() %>% 
  bvi_boxplot()

gridExtra::grid.arrange(plot2, plot3, ncol = 1)
```


# Discussion and Conclusions

# References

<div id="refs"></div>

# Figures and Tables


